### 2013-07-22 doc/asplos14/intro.tex
Rework end of intro to be more clear about how some MPI beats us (and reorder these)

We believe we can support irregular applications with good performance and cost effectively with commodity hardware for two main reasons. First, commodity multicore processors have become extremely fast with high clock rates, large caches and robust DRAM bandwidth. Second, commodity networks offer high bandwidth so long as messages are large enough. We build on these two observations and develop \Grappa, a software runtime system that allows a commodity cluster of x86-based nodes connected via an InfiniBand network to be programmed as if it were a single, large, shared-memory NUMA (non-uniform memory access) machine with scalable performance for irregular applications. \Grappa exploits fast processors and the memory hierarchy to provide a lightweight user-level tasking layer that supports a context switch in as little as 38ns and can sustain a large number of active workers. It bridges the commodity network bandwidth gap with a communication layer that combines short messages originating from a large number of active workers into larger ones.

@@

Our evaluation of \Grappa shows that its core components provide scalable performance for irregular applications.  It can multiplex thousands of workers on a multicore CPU and is limited only by DRAM bandwidth, not latency, to fetch worker state.  The communication layer helps \Grappa achieve over 1.0 Giga-Updates per second (GUPS) with 64 system nodes. Comparing \Grappa and native MPI implementations for more complex kernels is more complex.  When the MPI implementation is carefully tuned to aggregate messages in application code -- essentially duplicating the work \Grappa is doing for the programmer, without the generality and context switch overhead -- then the MPI implementation is between \checkme{6-10X} faster.  We see this in our comparisons for breadth first search and integer sorting.  On the other hand, if the MPI version is implemented in a straightforward manner, as we see with PageRank, GUPS, and unbalanced tree search, \Grappa is 2-5X faster.  When we compare \Grappa to the custom Cray XMT, we find \Grappa to be between 2.6X faster and 4.3X slower depending on the benchmark.

 \TODO{appA and tuned compared to appB and untuned is not ideal}

>>>>

We believe we can support irregular applications with good performance and cost effectively with commodity hardware for two main reasons. First, commodity multicore processors have become extremely fast with high clock rates, large caches and robust DRAM bandwidth. Second, commodity networks offer high bandwidth as long as messages are large enough. We build on these two observations and develop \Grappa, a software runtime system that allows a commodity cluster of x86-based nodes connected via an InfiniBand network to be programmed as if it were a single, large, shared-memory NUMA (non-uniform memory access) machine with scalable performance for irregular applications. \Grappa exploits fast processors and the memory hierarchy to provide a lightweight user-level tasking layer that supports a context switch in as little as 38ns and can sustain a large number of active workers. It bridges the commodity network bandwidth gap with a communication layer that combines short messages originating from many concurrent workers into larger packets.

@@

Our evaluation of \Grappa shows that its core components provide scalable performance for irregular applications.  It can multiplex thousands of workers on a multicore CPU and is limited only by DRAM bandwidth, not latency, to fetch worker state.  The communication layer helps \Grappa achieve over 1.0 Giga-Updates Per Second (GUPS) with 64 system nodes. Comparing \Grappa and native MPI implementations for more complex kernels is nuanced. Some applications use MPI in a straightforward manner, such as GUPS, PageRank, and Unbalanced Tree Search, for which \Grappa is 2-5X faster. On the other hand, some MPI implementations of irregular applications recognize its limitations and are written specially to aggregate messages and do some communication asynchronously, performing much the same work \Grappa does behind the scenes, but without paying the cost of generality imposed by context switches or message serialization, to name a few. We see this in our comparisons for Breadth First Search and Integer Sort, where the MPI implementation is \checkme{6-10X} faster.
When we compare \Grappa to the custom Cray XMT, we find \Grappa to be between 2.6X faster and 4.3X slower depending on the benchmark.
 \TODO{appA and tuned compared to appB and untuned is not ideal}
